\addcontentsline{toc}{chapter}{References}
\begin{thebibliography}{}
\bibitem{one}Andres Montes de OcaLuis, Arreola Alejandro, FloresShow, Gerardo Flores, "Low-cost multispectral imaging system for crop monitoring" in Conference: ICUAS'18 The 2018 International Conference on Unmanned Aircraft Systems at Dallas, TX, USA, May 2018

\bibitem{two}Adao, T., Hruska, J., Padua, L., Bessa, J., Peres, E., Morais, R. Sousa, J.J., " Hyperspectral Imaging: A Review on UAV-Based Sensors, Data Processing and Applications for Agriculture and Forestry." in Remote Sens. 2017, 9, 1110. 

\bibitem{eight-icuas}A. M. Jensen, M. Baumann, and Y. Chen, "Low-cost multispectral aerial imaging using autonomous runway-free small flying wing vehicles," in IGARSS 2008 - 2008 IEEE International Geoscience and Remote Sensing Symposium, vol. 5, July 2008, pp. V - 506-V - 509

\bibitem{two-remotev2}Park, S., Nolan, A., Ryu, D.; Fuentes, S., Hernandez E., Chung, H., O'Connell M., " Estimation of crop water stress in a nectarine orchard using high-resolution imagery from unmanned aerial vehicle (UAV)" In Proceedings of the 21st International Congress on Modelling and Simulation, Gold Coast, Australia, 29 November-4 December 2015; pp. 14131419. 

\bibitem{three-remotev2}Primicerio, J., Gennaro, S.F. D., Fiorillo E., Genesio, L., Lugato, E., Matese, A., Vaccari, F.P., "A flexible unmanned aerial vehicle for precision agriculture" Precis. Agric. 2012, 13, 517-523

\bibitem{fourteen-remotev2}Multispectral vs. Hyperspectral Imagery Explained. Available online: http://gisgeography.com/ multispectral-vs-hyperspectral-imagery-explained/ (accessed on 15 September 2017). 

\bibitem{fifteen-remotev2}Proctor C., He, Y., " Workﬂow for Building A Hyperspectral Uav: Challenges And Opportunities", ISPRS Int. Arch. Photogramm. Remote Sens. Spat. Inf. Sci. 2015, XL-1/W4, 415-419. 

\bibitem{stats1} Sushruth Sunder, \href{https://www.financialexpress.com/budget/india-economic-survey-2018-for-farmers-agriculture-gdp-msp/1034266/}{"India economic survey 2018: Farmers gain as agriculture mechanisation speeds up, but more R\&D needed"}, The Financial Express. 29 January 2018.  

\bibitem{stats2}\href{http://www.indiawaterreview.in/Story/Features/india-outranks-us-china-with-worlds-highest-net-cropland-area/2096/2#.W_A_iOgzZPY}{"India outranks US, China with world's highest net cropland area", India Water Review, 17 November 2018.}

\bibitem{eighth}Rustowicz, Rose M.. "Crop Classification with Multi-Temporal Satellite Imagery." (2017)

\bibitem{stats3}Sanjay Sharma, \href{https://timesofindia.indiatimes.com/india/62-farmers-cannot-meet-educational-needs-Survey/articleshow/12049496.cms}{"62\% farmers cannot meet educational needs: Survey"}, TNN, Times Of India, 2012


\end{thebibliography}
